Investigating Interventions

### 2025-01-23 minos/outcomes/spatial_analysis.Rmd
grepping sf12 to sf12mcs

# ggplot(full_pop_data, aes(x = SF_12, colour = is_green)) +

@@

# ggsave(here::here("plots","EPCG_SF_12.pdf"), plot=last_plot())

@@

<!-- baseline_2025 <- baseline_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
<!-- epcg_2025 <- epcg_2025[, c("hh_income", "SF_12", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->

@@

<!-- ggplot(plot_data, aes(x = SF_12, colour = group)) + -->
<!--   geom_density() -->

>>>>

# ggplot(full_pop_data, aes(x = SF_12_MCS, colour = is_green)) +

@@

# ggsave(here::here("plots","EPCG_SF_12_MCS.pdf"), plot=last_plot())

@@

<!-- baseline_2025 <- baseline_2025[, c("hh_income", "SF_12_MCS", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->
<!-- epcg_2025 <- epcg_2025[, c("hh_income", "SF_12_MCS", "SF_12_PCS", "yearly_energy", "heating", "housing_quality", "neighbourhood_safety")] -->

@@

<!-- ggplot(plot_data, aes(x = SF_12_MCS, colour = group)) + -->
<!--   geom_density() -->

### 2025-01-23 minos/validation/handovers_inflated.Rmd
grepping sf12 to sf12mcs

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12')
handover_lineplots(raw.dat, base.dat, "SF_12")
# 
# raw.sf12 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# # merge before plot
# sf12 <- rbind(raw.sf12, base.sf12)
# 
# # Now plot
# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_smooth() +
#   #geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
#   xlab('Year') +
#   ylab('SF12')
# 
# ## Try a version where final_US is limited to only those present from wave 1 
# # onwards because the sample refreshments are messing with the plot
# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.sf12.2 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12.2 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
# 
# # Now plot
# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
#   xlab('Year') +
#   ylab('SF12')
# 
# if (shall.we.save) {
#   ggsave(filename = 'SF12_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
```

>>>>

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
handover_lineplots(raw.dat, base.dat, "SF_12_MCS")
# 
# raw.sf12 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12_MCS) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12_MCS) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# # merge before plot
# sf12 <- rbind(raw.sf12, base.sf12)
# 
# # Now plot
# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_smooth() +
#   #geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
#   xlab('Year') +
#   ylab('SF12')
# 
# ## Try a version where final_US is limited to only those present from wave 1 
# # onwards because the sample refreshments are messing with the plot
# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.sf12.2 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12_MCS) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12.2 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12_MCS) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
# 
# # Now plot
# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
#   xlab('Year') +
#   ylab('SF12')
# 
# if (shall.we.save) {
#   ggsave(filename = 'SF12_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
```

### 2025-01-23 minos/validation/interventions.Rmd
grepping sf12 to sf12mcs

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)
income.energy <- energy %>% 
  select(pidp, time, hh_income, income_boosted)
# first rename and cbind
income.b <- rename(income.base, base = hh_income)
income.e <- rename(income.energy, energy = hh_income)
income.merged <- merge(income.b, income.e, by=c('pidp', 'time'))
income.merged <- pivot_longer(data = income.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'hh_income')
income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))
ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```
## SF_12
```{r}
sf12.base <- base %>% 
  select(pidp, time, SF_12)
sf12.energy <- energy %>% 
  select(pidp, time, SF_12, income_boosted)
# first rename and cbind
sf12.b <- rename(sf12.base, base = SF_12)
sf12.e <- rename(sf12.energy, energy = SF_12)
sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))
sf12.merged <- pivot_longer(data = sf12.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'SF_12')
sf12.merged.byyr <- sf12.merged %>%
  group_by(time, scenario) %>%
  summarise(SF_12 = mean(SF_12))
ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
  geom_line()
```

@@

>>>>

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)
income.energy <- energy %>% 
  select(pidp, time, hh_income, income_boosted)
# first rename and cbind
income.b <- rename(income.base, base = hh_income)
income.e <- rename(income.energy, energy = hh_income)
income.merged <- merge(income.b, income.e, by=c('pidp', 'time'))
income.merged <- pivot_longer(data = income.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'hh_income')
income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))
ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```
## SF_12_MCS
```{r}
sf12.base <- base %>% 
  select(pidp, time, SF_12_MCS)
sf12.energy <- energy %>% 
  select(pidp, time, SF_12_MCS, income_boosted)
# first rename and cbind
sf12.b <- rename(sf12.base, base = SF_12_MCS)
sf12.e <- rename(sf12.energy, energy = SF_12_MCS)
sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))
sf12.merged <- pivot_longer(data = sf12.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'SF_12_MCS')
sf12.merged.byyr <- sf12.merged %>%
  group_by(time, scenario) %>%
  summarise(SF_12_MCS = mean(SF_12_MCS))
ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12_MCS, color=scenario)) +
  geom_line()
```

@@

## Poverty Line Child Uplift

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)
income.poverty <- poverty %>% 
  select(pidp, time, hh_income, income_boosted)
# first rename and cbind
income.b <- rename(income.base, base = hh_income)
income.e <- rename(income.poverty, poverty = hh_income)
income.merged <- merge(income.b, income.e, by=c('pidp', 'time'))
income.merged <- pivot_longer(data = income.merged,
                              cols = base:poverty,
                              names_to = 'scenario',
                              values_to = 'hh_income')
income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))
ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```
## SF_12_MCS
```{r}
sf12.base <- base %>% 
  select(pidp, time, SF_12_MCS)
sf12.poverty <- poverty %>% 
  select(pidp, time, SF_12_MCS, income_boosted)
# first rename and cbind
sf12.b <- rename(sf12.base, base = SF_12_MCS)
sf12.e <- rename(sf12.poverty, poverty = SF_12_MCS)
sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))
sf12.merged <- pivot_longer(data = sf12.merged,
                              cols = base:poverty,
                              names_to = 'scenario',
                              values_to = 'SF_12_MCS')
sf12.merged.byyr <- sf12.merged %>%
  group_by(time, scenario) %>%
  summarise(SF_12_MCS = mean(SF_12_MCS))
ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12_MCS, color=scenario)) +
  geom_line()
```

## Boost Amount
```{r}
income.poverty <- poverty %>% 
  select(pidp, time, hh_income, income_boosted, boost_amount)
income.poverty.byyr <- income.poverty %>%
  group_by(time) %>%
  summarise(boost_amount = mean(boost_amount))
ggplot(data = income.poverty.byyr, mapping = aes(x = time, y = boost_amount)) +
  geom_line()
```
## Who Boosted?

```{r}
boosted.byyr <- income.poverty %>% 
  group_by(time) %>%
  count(income_boosted)
ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
  geom_line()
```
